Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way shown in Figure~\ref{fig:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time and $O(n)$ space.

@@

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \nn
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in time $O(n \log n + |S|)$ and space $O(n + |S|)$.

@@

    \item {\em left-bounded} by $r_b$, if the left edge of $B$ is a part of the left boundary of $r_b$ for some $b \in [k-2]$.
}
Figure~\ref{fig:type1}(b) shows an example with rectangles $r_1, r_2$, and $r_3$ (here $k = 5$). Their intersection is the gray rectangle $B$, which is bottom-bounded by $r_2$ and left-bounded by $r_3$.

@@

We aim to compute 
\myitems{
    \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$; 
    \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
}
In Figure~\ref{fig:type1}(b), $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2, v_3}$. As mentioned before, $r_a = r_2$ and $r_b = r_3$. We have $\cross(r_a, B; H) = \set{h_1, h_2}$ and $\cross(r_b, B; V) = \set{v_1, v_3}$. Note that $h_3$ is not in $\cross(r_a, B; H)$ because $h_3$ does not cross $B$, and $v_2$ is not in $\cross(r_b, B; V)$ because $v_2$ does not cross $r_3$.

@@

\mytab{
    \> {\bf algorithm generate-$S$} \\
    \> 1.\> $S = \emptyset$ \\ 
    \> 2.\> {\bf for} each $(r_1, ..., r_{k-2}) \in \Pi_{1:k-2}(\J_1(R_1,$ $...,$ $R_{k-2}, H, V))$ {\bf do} \\
    \> 3.\>\> define $B, r_a$, and $r_b$ as above \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(r_a, B; H) \times cross(r_b, B; V)$ {\bf do} \\
}

@@

\begin{figure} 
    \begin{tabular}{cc}
            \hspace{-3mm}
            \includegraphics[height=30mm]{./artwork/four-segs} &
            \hspace{-5mm}
            \includegraphics[height=37mm]{./artwork/oracle} \\ 
            \hspace{-3mm} (a) Constructing $r_1'$ from $r_1$ & 
            \hspace{-5mm} (b) Crossing oracles
    \end{tabular}
    \figcapup
    \caption{Illustrations for Section~\ref{sec:hv:type1}}
    \label{fig:type1}
    \figcapdown
\end{figure}

@@

>>>>

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way shown in Figure~\ref{fig:hv:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time and $O(n)$ space.

@@

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \label{eqn:hv:type1:S}
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in time $O(n \log n + |S|)$ and space $O(n + |S|)$.

@@

    \item {\em left-bounded} by $r_b$, if the left edge of $B$ is a part of the left boundary of $r_b$ for some $b \in [k-2]$.
}
Figure~\ref{fig:hv:type1}(b) shows an example with rectangles $r_1, r_2$, and $r_3$ (here $k = 5$). Their intersection is the gray rectangle $B$, which is bottom-bounded by $r_2$ and left-bounded by $r_3$.

@@

We aim to compute 
\myitems{
    \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$; 
    \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
}
In Figure~\ref{fig:hv:type1}(b), $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2, v_3}$. As mentioned before, $r_a = r_2$ and $r_b = r_3$. We have $\cross(r_a, B; H) = \set{h_1, h_2}$ and $\cross(r_b, B; V) = \set{v_1, v_3}$. Note that $h_3$ is not in $\cross(r_a, B; H)$ because $h_3$ does not cross $B$, and $v_2$ is not in $\cross(r_b, B; V)$ because $v_2$ does not cross $r_3$.

@@

\mytab{
    \> {\bf algorithm generate-$S$} \\
    \> 1.\> $S = \emptyset$ \\ 
    \> 2.\> {\bf for} each $(r_1, ..., r_{k-2}) \in \Pi_{1:k-2}(\J_1(R_1,$ $...,$ $R_{k-2}, H, V))$ {\bf do} \\
    \> 3.\>\> define $B, r_a$, and $r_b$ as above \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(r_a, B; H) \times \cross(r_b, B; V)$ {\bf do} \\
    \> 5.\>\>\> add $(r_1, ..., r_{k-2}, h, v)$ to $S$
}

\noindent In Appendix~\ref{app:hv:type1:gen-S}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired.

@@

\begin{figure} 
    \begin{tabular}{cc}
            \hspace{-3mm}
            \includegraphics[height=30mm]{./artwork/four-segs} &
            \hspace{-5mm}
            \includegraphics[height=37mm]{./artwork/oracle} \\ 
            \hspace{-3mm} (a) Constructing $r_1'$ from $r_1$ & 
            \hspace{-5mm} (b) Crossing oracles
    \end{tabular}
    \figcapup
    \caption{Illustrations for Section~\ref{sec:hv:type1}}
    \label{fig:hv:type1}
    \figcapdown
\end{figure}

@@

\section{Correctness of Algorithm generate-S} \label{app:hv:type1:gen-S}
